Welch-Lynch clock synchronization protocol \\\textit{Modelling in UPPAAL}

### 2013-04-16 paper/main.tex
Finalized optimizations, added captions and third bibtex entry

\begin{figure}[!h]
\includegraphics[width=\textwidth]{original_process}
\label{fig:original_process}
\end{figure}

@@

\begin{figure}[!h]
\includegraphics[width=\textwidth]{step1_process}
\label{fig:step1_process}
\end{figure}

@@

\item \textbf{Specific three process instance} \\
	In 2004, it was probably noticed that it turned out to be hard to verify instances of the protocol using \UPPAAL. Therefore, the researchers tried to restrict themselves to three processes. This allows for a more direct computation of the minimum and maximum values in the right part of the process automaton. The variables \texttt{ARR1}, \texttt{min1} and \texttt{max1} are replaced by a single variable \texttt{SUM}. Removing variables implies reducing the search space.

@@

\begin{figure}[!h]
\includegraphics[width=\textwidth]{step3minimized_process}
\label{fig:step3minimized_process}
\end{figure}

\item \textbf{Symmetry reduction} \\
%TODO

\item \textbf{Extended guards} \\
%TODO
\end{enumerate}

>>>>

\begin{figure}[!h]
\includegraphics[width=\textwidth]{original_process}
\caption{Process in \texttt{original.xml}\label{fig:original_process}}
\end{figure}

@@

\begin{figure}[!h]
\includegraphics[width=\textwidth]{step1_process}
\caption{Process in \texttt{step1.xml}\label{fig:step1_process}}
\end{figure}

@@

\item \textbf{Specific three process instance} \\
	In 2004, it was presumably noticed that it turned out to be hard to verify instances of the protocol using \UPPAAL. Therefore, the researchers tried to restrict themselves to three processes. This allows for a more direct computation of the minimum and maximum values in the right part of the process automaton. The variables \texttt{ARR1}, \texttt{min1} and \texttt{max1} are replaced by a single variable \texttt{SUM}. Removing variables implies reducing the search space.

@@

\begin{figure}[!h]
\includegraphics[width=\textwidth]{step3minimized_process}
\caption{Process in \texttt{step3minimized.xml}\label{fig:step3minimized_process}}
\end{figure}

\item \textbf{Symmetry reduction} \\
	Symmetry reduction \cite{Hendriks2004Adding} is a powerful technique to drastically reduce both computation time and memory usage. This reduction is exponential in the size of the scalar sets, a symmetric data type, that are used. The processes in the protocol are highly symmetrical. When their IDs are defined as a scalar set type, the \UPPAAL verifier can use so-called \textit{state swaps} to reduce the state space. For instance, their used to be lots of different orders in which the \texttt{local\_time} counter could be incremented. Using symmetry reduction, the order is not important anymore.

\item \textbf{Extended guards} \\
	The channel automaton used to contain a variable \(C\) that counted how many messages had been received. When all messages had been received, another transition could be taken. This variable has been removed completely, due to a richer syntax which allows for guards with \texttt{forall} modifiers. Now it's easier to check if all messages have been received, i.e. if all boolean values in an array are set to true. In figure~\ref{fig:original_channel}, one can see the original channel, while figure~\ref{fig:step4scalar_channel} shows the optimized automaton.

\begin{figure}[!h]
\includegraphics[scale=0.7]{original_channel}
\caption{Channel in \texttt{original.xml}\label{fig:original_channel}}
\end{figure}

\begin{figure}[!h]
\includegraphics{step4scalar_channel}
\caption{Channel in \texttt{step4scalar.xml}\label{fig:step4scalar_channel}}
\end{figure}

\end{enumerate}
